A general model for the evolution of nuptial gift-giving

### 2024-06-15 ms_refs_fixed.Rmd
Tweak the supporting information captions to fix the replicate number

---
title: "A general model for the evolution of nuptial gift-giving"
author: |
  | Anders P. Charmouh$^{1,4, 5}$, Trine Bilde$^{2}$, Greta Bocedi$^{1}$, A. Bradley Duthie$^{3}$
date: '[1] School of Biological Sciences, University of Aberdeen, UK. [2] Department of Biology, Aarhus University, Denmark. [3] Biological and Environmental Sciences, University of Stirling, UK.  [4] Bioinformatics Research Centre Aarhus University, University City 81, building 1872, 3rd floor, DK-8000 Aarhus C, Denmark [5] Email: apc@birc.au.dk'
output:
  html_document: default
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution-letters.csl
    reference_docx: docx_template.docx
bibliography: nuptial_refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage{caption}
- \usepackage[utf8]{inputenc}
- \bibliographystyle{amnatnat}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 2
link-citations: yes
linkcolor: blue
csl: evolution-letters.csl
biblio-style: apalike
---

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively). The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red). The results show noise, but no correlation between the value of the mortality parameters and the propensity for male search and/or female choice to evolve. For each of the $25 \\times 20$ combinations of $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$, 1600 replicate simulations were run."}
SUMO <- read.csv("inst/SI_mortality.csv");
mort_combn   <- paste(SUMO[,1], SUMO[,2]);
mort_label   <- unique(paste(SUMO[,1], ", ", SUMO[,2], sep = ""));
TM_vals      <- tapply(X = SUMO[,4],  INDEX = mort_combn, FUN = mean);
m_vals       <- tapply(X = SUMO[,14], INDEX = mort_combn, FUN = mean);
beta_vals    <- tapply(X = SUMO[,15], INDEX = mort_combn, FUN = mean);
Male_M       <- tapply(X = SUMO[,16], INDEX = mort_combn, FUN = mean);
Female_M     <- tapply(X = SUMO[,17], INDEX = mort_combn, FUN = mean);
Mf_nupt      <- tapply(X = SUMO[,18], INDEX = mort_combn, FUN = mean);
Mf_nonupt    <- tapply(X = SUMO[,19], INDEX = mort_combn, FUN = mean);
male_search  <- as.numeric(which(SUMO[,5] > 0 & SUMO[,6] > 0));
fem_choose   <- as.numeric(which(SUMO[,8] > 0 & SUMO[,9] > 0));
mimmom       <- unique(cbind(SUMO[,1], SUMO[,2]));

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.2 ($T_{\\mathrm{f}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=0.5$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
SUMM_Tf0pt4 <- read.csv("inst/SI_Tf_0pt5.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations include fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=10.0$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
SUMM_Tf10 <- read.csv("inst/SI_Tf_10pt0.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations had fewer replicates, minimum 400). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 1000 interactions occur between individuals in each time step ($\\psi = 1$), potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp1   <- read.csv("inst/SI_Nexp_1.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 2000 interactions occur between individuals in each time step ($\\psi = 2$), potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp2   <- read.csv("inst/SI_Nexp_2.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 4000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 4$). The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp4   <- read.csv("inst/SI_Nexp_4.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 6$). The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp6   <- read.csv("inst/SI_Nexp_6.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.8 ($T_{\\mathrm{m}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 1600 replicate simulations with identical starting conditions. The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts). Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$). The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Tm05   <- read.csv("inst/SI_Tm_0pt5.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.9 ($T_{\\mathrm{m}} = 2.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 1600 replicate simulations with identical starting conditions. The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts). Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$). The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Tm2p5   <- read.csv("inst/SI_Tm_2pt5.csv");

>>>>

---
title: "A general model for the evolution of nuptial gift-giving"
author: |
  | Anders P. Charmouh$^{1,4, 5}$, Trine Bilde$^{2}$, Greta Bocedi$^{1}$, A. Bradley Duthie$^{3}$
date: '[1] School of Biological Sciences, University of Aberdeen, UK. [2] Department of Biology, Aarhus University, Denmark. [3] Biological and Environmental Sciences, University of Stirling, UK.  [4] Bioinformatics Research Centre Aarhus University, University City 81, building 1872, 3rd floor, DK-8000 Aarhus C, Denmark [5] Email: apc@birc.au.dk'
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution-letters.csl
    reference_docx: docx_template.docx
bibliography: nuptial_refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage{caption}
- \usepackage[utf8]{inputenc}
- \bibliographystyle{amnatnat}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 2
link-citations: yes
linkcolor: blue
csl: evolution-letters.csl
biblio-style: apalike
---

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively). The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red). The results show noise, but no correlation between the value of the mortality parameters and the propensity for male search and/or female choice to evolve. For each of the $25 \\times 20$ combinations of $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$, 1600 replicate simulations were run."}
SUMO <- read.csv("inst/SI_mortality.csv");
mort_combn   <- paste(SUMO[,1], SUMO[,2]);
mort_label   <- unique(paste(SUMO[,1], ", ", SUMO[,2], sep = ""));
TM_vals      <- tapply(X = SUMO[,4],  INDEX = mort_combn, FUN = mean);
m_vals       <- tapply(X = SUMO[,14], INDEX = mort_combn, FUN = mean);
beta_vals    <- tapply(X = SUMO[,15], INDEX = mort_combn, FUN = mean);
Male_M       <- tapply(X = SUMO[,16], INDEX = mort_combn, FUN = mean);
Female_M     <- tapply(X = SUMO[,17], INDEX = mort_combn, FUN = mean);
Mf_nupt      <- tapply(X = SUMO[,18], INDEX = mort_combn, FUN = mean);
Mf_nonupt    <- tapply(X = SUMO[,19], INDEX = mort_combn, FUN = mean);
male_search  <- as.numeric(which(SUMO[,5] > 0 & SUMO[,6] > 0));
fem_choose   <- as.numeric(which(SUMO[,8] > 0 & SUMO[,9] > 0));
mimmom       <- unique(cbind(SUMO[,1], SUMO[,2]));

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.2 ($T_{\\mathrm{f}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=0.5$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
SUMM_Tf0pt4 <- read.csv("inst/SI_Tf_0pt5.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations include fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=10.0$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
SUMM_Tf10 <- read.csv("inst/SI_Tf_10pt0.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from approximately 100 replicate simulations with identical starting conditions (some parameter combinations had fewer replicates, minimum 400). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 1000 interactions occur between individuals in each time step ($\\psi = 1$), potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp1   <- read.csv("inst/SI_Nexp_1.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 2000 interactions occur between individuals in each time step ($\\psi = 2$), potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp2   <- read.csv("inst/SI_Nexp_2.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 4000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 4$). The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp4   <- read.csv("inst/SI_Nexp_4.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates). Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Up to 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 6$). The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp6   <- read.csv("inst/SI_Nexp_6.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.8 ($T_{\\mathrm{m}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 1600 replicate simulations with identical starting conditions. The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts). Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$). The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Tm05   <- read.csv("inst/SI_Tm_0pt5.csv");

@@

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.9 ($T_{\\mathrm{m}} = 2.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 1600 replicate simulations with identical starting conditions. The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts). Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$). The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Tm2p5   <- read.csv("inst/SI_Tm_2pt5.csv");
